Component response rate variation underlies the stability of complex systems

### 2020-03-11 notebook/ms.Rmd
Write a paragraph on structured networks in the Results

>>>>

**Simulation of structured $\mathbf{M}$ across $\mathbf{S}$**.

To investigate how $\sigma^{2}_{\gamma}$ affects stability for different network structures, I simulated $\mathbf{M}$ with fixed properties across $S$. This included three types of random networks that are typically interpreted in terms of differing interspecific ecological interaction types [@Allesina2011; @Allesina2012]. These interactions types are competitive, mutualist, or predator-prey, as modelled by off-diagonal elements of $\mathbf{M}$ that are constrained to be negative, positive, or paired such that if $A_{ij} > 0$ then $A_{ji} < 0$, respectively [@Allesina2012]. I also simulated three commonly observed system structures, including cascade food webs [@Williams2000], small-world networks [@Watts1998], and scale-free networks [@Albert2002]. For all except mutualist networks, as $S$ increased, a higher number of stable systems were observed given $\sigma^{2}_{\gamma}>0$ versus $\sigma^{2}_{\gamma}=0$.
